---
title: "FunctionsForSimuDataPreProc"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

# Setup
pacman::p_load(tidyverse,
               Rfast, 
               geodist,
               ggplot2,
               igraph,
               RColorBrewer)

```

# Function for making the studygroup (ingroup) vs non-studygroup (outgroup) connections overview 

This function below needs two inputs, and it returns three dataframes available for access. 

* edgelistcsv, as in e.g. ABM_24May_edges <- read.csv("ABM_24May_high_SG_edgelist_Pernille.csv")
* populationcsv, as in e.g. population_24May <- read.csv("population_24May_Pernille.csv") # here are the studygroups

*Remember to rename the dataframes outputted if you're making more of these in a row.*

## The function
```{r}
get_in_and_outgroups <- function(edgelistcsv,populationcsv){ # Before putting it in, read in the population + edgelist in csv
  
  # population
  populationcsv <- tibble::rowid_to_column(populationcsv, "ID")
  populationcsv <- populationcsv %>% rename(studygroup_no = studygroup)
  populationcsv$ID <- as.factor(populationcsv$ID)
  
  population_df <- populationcsv
  
  # edges
  edges_df <- edgelistcsv %>% rename(to = V1,
                                        from = V2)
  
  # rename so it's easier
  studygroup_membership_population <- population_df %>% rename(membership=studygroup_no)

  # take "from" column 
  studygroup_membership_population1 <- studygroup_membership_population %>% rename(from = ID)

  # Merge
  studygroup_membership_population_temp <- merge(edges_df, studygroup_membership_population1, by = "from")

  # Take "to" column 
  studygroup_membership_population2 <- studygroup_membership_population %>% rename(to = ID)

  # Merge
  edges_and_studygroups <- merge(studygroup_membership_population_temp,studygroup_membership_population2, by = "to" )

  # Renaming the columns we just got
  edges_and_studygroups_renamed <- edges_and_studygroups %>% rename(membership_from = membership.x)
  edges_and_studygroups <- edges_and_studygroups_renamed %>% rename(membership_to = membership.y)

  # Make a column indicating in/outgroup
  edges_and_studygroups$group <- ifelse(edges_and_studygroups$membership_to == edges_and_studygroups$membership_from, "ingroup", "outgroup")


  # Summarise and count grouped by from and to in order to get the right numbers after
  from <- edges_and_studygroups %>% group_by(from, group) %>% summarise(n = n())
  to <- edges_and_studygroups %>% group_by(to, group) %>% summarise(n = n())

  # Adding from and to together and binding them - they're going to be different instances anyway
  converted_to <- from %>% rename(to = from)
  connections <- rbind(to,converted_to)

  # Making subsets
  connections_in <- connections %>% filter(group=="ingroup")
  connections_out <- connections %>% filter(group=="outgroup")

  # Now, count + make a new column in both subsets so they can be put together
  connections_in <- connections_in %>% group_by(to) %>%
       summarize(SG_connections = sum(n)) %>% 
    mutate(NON_SG_connections = NA)

  connections_out <- connections_out %>% group_by(to) %>%
       summarize(NON_SG_connections = sum(n)) %>% 
    mutate(SG_connections = NA)

  # Merge (no NA's) + lastly replacing -Inf with 0's (those without studygroups or no outgoings)
  connections_overview <- rbind(connections_in,connections_out, fill = TRUE)
  
  edges_and_studygroups <- connections_overview %>%
    group_by(to) %>%
    summarise(
      NON_SG_connections = max(NON_SG_connections, na.rm = T),
      SG_connections = max(SG_connections, na.rm = T)
    )

  edges_and_studygroups[edges_and_studygroups == -Inf] <- 0


  edges_and_studygroups <- edges_and_studygroups %>% rename(outgroup = NON_SG_connections,
                                                            ingroup = SG_connections)
 
    # Finally, make it long
  long_edges_and_studygroups <- edges_and_studygroups %>%
   pivot_longer(c(outgroup, ingroup), names_to = "group") %>%
   rename(ID = to,
          count = value)
  
   # Making an extended version w. difference column, absolute difference, total connections, ratio out/total
  edges_and_studygroups_ext <- edges_and_studygroups %>%
    mutate(
      diff_in_out_connections = outgroup-ingroup,
      absdiff_in_out_connections = abs(outgroup-ingroup),
      total_connections = outgroup+ingroup,
      ratio_outgoing_over_total = outgroup/total_connections
    )
  
  # Saving two mains
  wide_edges_and_studygroups <<- edges_and_studygroups
  long_edges_and_studygroups <<- long_edges_and_studygroups
  
  # Evt: 
  # edges_and_studygroups_ext <<- edges_and_studygroups_ext 
  
  print("Nevermind the grouping warnings, but REMEMBER TO RENAME WIDE_EDGES..+ LONG_EDGES..")

}
```

# Function 2: Get the graph from edgelistcsv
```{r}

# Function
graph_from_edgelist_own <- function(edgelistcsv, u) {
  set.seed(123)
  
  edges <- edgelistcsv %>% rename(from = V1,
                                        to = V2) # theyre always named something weird when saved
  
  if (NCOL(edges) > 2){
    edges[,1] <- NULL
  }
  
  nodes <- data.frame(ID = unique(c(edges$from,
                                    edges$to)))
  
  # Using igraph to plot
  igraph_basic <-
    graph_from_data_frame(d = edges,
                          vertices = nodes,
                          directed = TRUE)
  
  igraph_simple_f <- simplify(
    igraph_basic,
    remove.multiple = TRUE,
    remove.loops = TRUE,
    edge.attr.comb = igraph_opt("edge.attr.comb")
  )
  
  V(igraph_simple_f)$frame.color <- "white"
  V(igraph_simple_f)$color <- "orange"
  #V(igraph_simple_f)$label <- "" # can be unhashed for difference
  E(igraph_simple_f)$arrow.mode <- 0 
  #E(igraph_simple_f)$width <- edge_attr(igraph_simple_f)$weight/2 # can be unhased for difference
  V(igraph_simple_f)$size <-
    degree(igraph_simple_f, mode = "all")
  
  igraph_simple_f <<- igraph_simple_f
  
  print("Remember to rename the graph object with the dates/info.")
  
  # First plot
  if (u == 1){
     wcf <- cluster_walktrap(igraph_simple_f)
     return(plot(wcf, igraph_simple_f) + title("First look at communities (using cluster walktrap)"))
  }
  
  if (u == 0){
    # Second plot
    clpf <- cluster_louvain(as.undirected(igraph_simple_f))
    return(plot(clpf, igraph_simple_f) + title("Second look at communities (using cluster_louvain)"))
  }
}

```

# Function 3: Getting network metrics from graph object
```{r}

# Function
get_network_metrics_from_graph <- function(graphobject) {
  
  # --------- DEGREE ---------
  
  degrees <-
    as.data.frame(degree(graphobject)) %>% rownames_to_column("ID")
  colnames(degrees)[2] <- "degrees"
  
  degrees_out <-
    as.data.frame(degree(graphobject, mode = "out")) %>% rownames_to_column("ID")
  colnames(degrees_out)[2] <- "degrees_out"
  
  degrees_in <-
    as.data.frame(degree(graphobject, mode = "in")) %>% rownames_to_column("ID")
  colnames(degrees_in)[2] <- "degrees_in"
  
  temp <- merge(degrees, degrees_out, by = "ID")
  
  degrees_f <- merge(temp, degrees_in, by = "ID")
  
  # Printing summaries
  print("Summary all degrees: ")
  print(summary(degrees_f$degrees))
  
  print("Summary indegrees: ")
  print(summary(degrees_f$degrees_in))
  
  print("Summary outdegrees: ")
  print(summary(degrees_f$degrees_out))
  
  
  # --------- BETWEENNESS ---------
  
  betweenness <-
    as.data.frame(betweenness(graphobject)) %>% rownames_to_column("ID")
  colnames(betweenness)[2] <- "betweenness"
  
  # Printing summaries
  print("Summary betweenness: ")
  print(summary(betweenness$betweenness))
  
  
  # --------- TRANSITIVITY ---------
  
  transitivity <-
    data.frame(node = names(V(graphobject)),
               trans = transitivity(graphobject, type = "local")) %>%
    rename(ID = node,
           transitivity = trans)
  
  # Printing summaries
  print("Summary transitivity: ")
  print(summary(transitivity$transitivity))
  
  # --------- EIGEN-CENTRALITY ---------
  
  eigencentrality <-
    as.data.frame(eigen_centrality(graphobject)) %>% rownames_to_column("ID")
  colnames(eigencentrality)[2] <- "eigen_centrality"
  
  eigencentrality <-
    eigencentrality %>% select(ID, eigen_centrality)
  
  # Printing summaries
  print("Summary eigen_centrality: ")
  print(summary(eigencentrality$eigen_centrality))
  
  
  # Merging all the dataframes from above into one networkmetrics-df
  temp <- merge(degrees_f, betweenness, by = "ID")
  temp <- merge(temp, transitivity, by = "ID")
  temp <- merge(temp, eigencentrality, by = "ID")
  
  NetworkMetrics_f <<- temp
  print("REMEMBER TO RENAME THE NetworkMetrics_f OBJECT!")
}
```

```{r}
# Assessing the two final ABM outputs - works as kind of a test
population_studygroups <- read.csv("population_w_studygroups.csv") # here are the study-groups

### C18
C18_ABM <- read_csv("C18ABM_SG15.csv")

graph_from_edgelist_own(C18_ABM,0)

get_in_and_outgroups(C18_ABM,population_studygroups)

C18_ABM_long <- long_edges_and_studygroups

C18_ABM_long %>% group_by(group) %>% summarise(mean = mean(count),
                                                               sd = sd(count))

###### C19
C19_ABM <- read_csv("C19ABM_SG15_LOCKDOWN_TRUE.csv")

graph_from_edgelist_own(C19_ABM,0)

get_in_and_outgroups(C19_ABM,population_studygroups)

C19_ABM_long <- long_edges_and_studygroups

C19_ABM_long %>% group_by(group) %>% summarise(mean = mean(count),
                                                               sd = sd(count))

```




